\documentclass[11pt]{article}
\usepackage{epsfig}
\usepackage{subfigure}
\usepackage{setspace}
\usepackage{url}

\setlength{\textheight}{8.875in} \setlength{\textwidth}{6.5in}
\setlength{\topmargin}{0.0in} \setlength{\headheight}{0.0in}
\setlength{\headsep}{0.0in} \setlength{\oddsidemargin}{0.0in}

\begin{document}
\pagestyle{empty}
\thispagestyle{empty}

\begin{center}
\textbf{\Large Budget Justification}
\end{center}

\subsection*{Personnel}
We request one half month of support per year for PI Chamberlain and Co-PIs
Ahrens and Gill.
We request support for two GRAs/year. Salaries are 
assumed to increase 3\%/year. 

\subsection*{Equipment}
We request \$10,000 in each of years 2 and 3 to build a pair of
prototype catoptric systems.  One will be installed at
BECS Technology, Inc. (10818 Midwest Industrial Dr., St. Louis, MO)
and the other will be installed at a location to be determined on
the Danforth campus of Washington Univ. in St. Louis.

\subsection*{Travel}
We request \$3600/year for senior personnel and student travel
to present our work at academic 
conferences and to attend the PI meetings.
This is based upon a plan for 3 individual trips
each year, with an expected cost of \$1200 per trip.
Candidate conferences include ACADIA, ICCPS, RTAS, etc.
We will also ensure that at least one PI/Co-PI is
at the annual PI meetings that are arranged by NSF. 

\subsection*{Participant Support Costs}
We request support for two REU students in year 1. 
The amount is set to match the support provided by the currently
running REU Site Grant, IIS-1560191, so that all NSF-supported REU
students in the department are compensated the same (as requested by
the program manager for the site grant).
For each student: \$5,000 stipend, \$1,200 food allowance, and \$2,350
housing allowance.

\subsection*{Materials and Supplies}
We request \$1,000/year for
miscellaneous components to both keep the experimental catoptric
infrastructure operational and to make alterations to it for
experimental purposes. This will
include additional computational components (e.g., microcontrollers, etc.)
as well as physical components (e.g., mirrors, structural elements, motors,
etc.).

\subsection*{Indirect costs}
Indirect costs are requested at Washington University's standard rate of
57\% of MTDC (starting 7/1/2019) and 57.5\% of MTDC (starting 7/1/2020).

\end{document}
